Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-19 cvx-flats-neurips21/cvx-flats.tex
typo
Edits in body from May 18 meeting

\usepackage{times}
\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts,amsmath,amssymb,amsthm}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

@@

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
These two scenarios typically involve different techniques for designing and analyzing surrogate losses.
We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension.
Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For continuous estimation, our lower bound resolves on open problem on estimating measures of risk and uncertainty.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

@@

\paragraph{Contributions}
First, we formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
We then show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
With these tools in hand, we present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) via indirect elicitation.
These bounds are the first to our knowledge that can be applied in all four quadrants.
Moreover, our framework can also give tighter bounds than previously existed in the literature.
We illustrate this sharpness with new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, CVaR, and other measures of risk and uncertainty (\S~\ref{sec:contin-consis}).
See Figure~\ref{fig:results-flow} for a roadmap of our main results.

@@

To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A surrogate loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \reals^d$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}
% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.

An important caveat to the above definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}

@@

\begin{theorem}\label{thm:consistent-implies-indir-elic}
  For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{theorem}

@@

\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
Theorem~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
\jessie{Edit this paragraph if Cors 2 and 3 move to the Appendix}

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
  Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.
  Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
%and in particular, $\conscvx(\gamma) \geq d + 1$. 
%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$, where $L\in\Lcvx_d$, and let $\Gamma = \prop{L}$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.
    If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\eliccvx(\gamma) \geq d+1$, and recall $\conscvx(\gamma) \geq \eliccvx(\gamma)$ by Corollary~\ref{cor:elic-lb-consis-dim}.
\end{proof}

@@

\section{Illustration: geometric intuition for the four quadrants}
\jessiet{At this rate, doesn't need to be in a section header of its own?}
We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2) and~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4).
This is demonstrated in Table~\ref{tab:quadrants-simplices}.
These illustrations are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.

\begin{table}
\begin{tabular}{|c|c|}
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

	\pgfmathsetmacro{\ph}{0.54}
	\pgfmathsetmacro{\pm}{0.23}
	\pgfmathsetmacro{\pl}{0.23}
	\coordinate (p) at (\ph,\pm,\pl);
	\coordinate (uniform) at (1/3,1/3,1/3);
	\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
	\coordinate[label=below:${y=1}$] (m) at (0,1,0);
	\coordinate[label=above:${y=0}$] (l) at (0,0,1);

	\pgfmathsetmacro{\ph}{0.54}
	\pgfmathsetmacro{\pm}{0.23}
	\pgfmathsetmacro{\pl}{0.23}
	\coordinate (p) at (\ph,\pm,\pl);
	\coordinate (uniform) at (1/3,1/3,1/3);
	\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
	\coordinate[label=below:${y=1}$] (m) at (0,1,0);
	\coordinate[label=above:${y=0}$] (l) at (0,0,1);

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue,thin] (2/3,0,1/3) -- (0,2/3, 1/3);
	\def\e{1/16};
	\draw[myblue,thin] (\e + 1/3, 1/3- \e,1/3) -- (1/2 + \e, 1/2 - \e,0);
	\coordinate (point) at (1/3 - \e/2, 1/3 + \e, 1/3 - \e/2);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[orange, dashed] (2/3 + \e/2,0,1/3 - \e/2) -- (0,2/3 + \e/2, 1/3 - \e/2);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\Gamma_{-1}\!\!$};
	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\Gamma_{1}\!\!$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
	\end{tikzpicture}
	\\
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

\pgfmathsetmacro{\ph}{0.54}
\pgfmathsetmacro{\pm}{0.23}
\pgfmathsetmacro{\pl}{0.23}
\coordinate (p) at (\ph,\pm,\pl);
\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
\coordinate[label=below:${y=1}$] (m) at (0,1,0);
\coordinate[label=above:${y=0}$] (l) at (0,0,1);

>>>>

\usepackage{times}
\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts,amsmath,amssymb,amsthm}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage{sidecap}

@@

\begin{abstract}
	\jessie{Revisit}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
These two scenarios typically involve different techniques for designing and analyzing surrogate losses.
We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension.
Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For continuous estimation, our lower bound resolves on open problem on estimating measures of risk and uncertainty.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

@@

\paragraph{Contributions}
First, we formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
We then show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
With these tools in hand, we present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}) via indirect elicitation.
These bounds are the first to our knowledge that can be applied in all four quadrants.
Moreover, our framework can also give tighter bounds than previously existed in the literature.
We illustrate this sharpness with new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, CVaR, and other measures of risk and uncertainty (\S~\ref{sec:contin-consis}).
See Figure~\ref{fig:results-flow} for a roadmap of our main results.
\jessie{Re-write}

\jessie{Broader impacts}

@@

To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A surrogate loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \reals^d$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}

While implicitly observed in some of the literature~\citep{steinwart2008support}\jessie{Add more}, we can observe that consistency implies indirect elicitation.
Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but we loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss or conditional statistical value.
\jessie{Make restateable}
\begin{proposition}\label{thm:consistent-implies-indir-elic}
	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{proposition}

% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.

An important caveat to the above elicitation definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
From Theorem \ref{thm:consistent-implies-indir-elic}, in Appendix~\ref{sec:consis-implies-indir}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
%We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
Lemma~\ref{lem:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
Lemma~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
\jessie{Edit this paragraph if Cors 2 and 3 move to the Appendix}

\subsection{Illustration: geometric intuition for the four quadrants}
\jessiet{At this rate, doesn't need to be in a section header of its own?}
We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2) and~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4).
This is demonstrated in Table~\ref{tab:quadrants-simplices}.\jessie{Ref is wrong}
These illustrations are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.

\begin{SCtable}
\begin{tabular}{|c|c|}
	\hline
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

	\pgfmathsetmacro{\ph}{0.54}
	\pgfmathsetmacro{\pm}{0.23}
	\pgfmathsetmacro{\pl}{0.23}
	\coordinate (p) at (\ph,\pm,\pl);
	\coordinate (uniform) at (1/3,1/3,1/3);
	\coordinate[label=below:${y_1}$] (h) at (1,0,0);
	\coordinate[label=below:${y_3}$] (m) at (0,1,0);
	\coordinate[label=right:${y_2}$] (l) at (0,0,1);

	\pgfmathsetmacro{\ph}{0.54}
	\pgfmathsetmacro{\pm}{0.23}
	\pgfmathsetmacro{\pl}{0.23}
	\coordinate (p) at (\ph,\pm,\pl);
	\coordinate (uniform) at (1/3,1/3,1/3);
	\coordinate[label=below:${y_1}$] (h) at (1,0,0);
	\coordinate[label=below:${y_3}$] (m) at (0,1,0);
	\coordinate[label=right:${y_2}$] (l) at (0,0,1);

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue,thin] (2/3,0,1/3) -- (0,2/3, 1/3);
	\def\e{1/16};
	\draw[myblue,thin] (\e + 1/3, 1/3- \e,1/3) -- (1/2 + \e, 1/2 - \e,0);
	\coordinate (point) at (1/3 - \e/2, 1/3 + \e, 1/3 - \e/2);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[orange, dashed] (2/3 + \e/2,0,1/3 - \e/2) -- (0,2/3 + \e/2, 1/3 - \e/2);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\Gamma_{-1}\!\!$};
	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\Gamma_{1}\!\!$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
	\end{tikzpicture}
	\\
	\hline
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

\pgfmathsetmacro{\ph}{0.54}
\pgfmathsetmacro{\pm}{0.23}
\pgfmathsetmacro{\pl}{0.23}
\coordinate (p) at (\ph,\pm,\pl);
\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
\coordinate[label=below:${y=1}$] (m) at (0,1,0);
\coordinate[label=right:${y=0}$] (l) at (0,0,1);

\pgfmathsetmacro{\ph}{0.54}
\pgfmathsetmacro{\pm}{0.23}
\pgfmathsetmacro{\pl}{0.23}
\coordinate (p) at (\ph,\pm,\pl);
\coordinate[label=below:${y=-1\!\!\!\!}$] (h) at (1,0,0);
\coordinate[label=below:${y=1}$] (m) at (0,1,0);
\coordinate[label=right:${y=0}$] (l) at (0,0,1);

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.1,...,1}
{
	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
	\pgfmathsetmacro\bb{0.5*\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(1-\aa,\aa,0)$);
	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
	\draw[myblue,thin] (C) parabola (A);
	\draw[myblue,thin] (C) parabola (B);
}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\coordinate (A) at ($(\aa,1-\aa,0)$);
\coordinate (B) at ($(1-\aa,\aa,0)$);
\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
\coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
\coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
\coordinate (centerdot) at (0.3,0.3, 0.4);
\draw[myorange, very thick] (C) parabola (A);
\draw[myorange, very thick] (C) parabola (B);
\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (3/4,0,1/4) -- (centerdot);
\node at (centerdot) {$\bullet$};
\end{scope}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.6}$};
\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
\placefiglabel{(Q4)}
\end{tikzpicture}
\\
\hline
\end{tabular}\label{tab:quadrants-simplices}
\caption{Example properties for each of the quadrants. 
In (Q1), we fix $p$ uniform in the abstain level set $\Gamma_\bot$. 
We cannot fit a line ($1$-flat) through $p$ without leaving the level set $\Gamma_\bot$.  
Therefore, there is no $1$-dimensional consistent convex surrogate for abstain by Lemma~\ref{lem:convex-flats-inf-dim}.  
(Q2) is similar to (Q1) but has no target loss since it is not elicitable.
In (Q3), we can fit a $1$-flat through any $p \in \simplex$ for least squares, eliciting expected value.
In (Q4), we look at the variance, and take the distribution $p = \bullet \in \Gamma_{0.6}$.
Since $\Gamma_{0.6}$ (solid orange) is curved, we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t. the variance.
}
\end{SCtable}

\subsection{Breadth of framework: Discrete-valued predictions}\label{sec:discrete-predictions-refactored}

In Quadrant 1,~\citet{ramaswamy2016convex} give a lower bound on convex consistency dimension roughly by the co-dimension of the \emph{subspace of feasible directions} $\Sc_{\C}(p)$ of a convex set $\C$ at a given distribution $p$ such that $p \in \C$, which is loosely the ``most full'' subspace of $\C$ containing a neighborhood around $p$.

\begin{equation*}\label{eq:feasible-subspace}
\Sc_\C(p) = \{v \in \reals^n \mid \exists \epsilon_0 > 0 \textrm{ such that } p + \epsilon v \in \C\forall \epsilon \in (-\epsilon_0, \epsilon_0) \}
\end{equation*}

Our Lemma~\ref{lem:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Lemma~\ref{lem:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.

\begin{proposition}\label{prop:discrete-bound-subsumes-ramaswamy}
	Suppose we are given a discrete loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma: \simplex \toto \R$.
	Fix $p \in \relint \simplex$ and take $r \in \R$ such that $p \in \gamma_r$.  
	If $\conscvx(\ell) = d$, then there exists a $d$-flat $F \subseteq \gamma_r$ through $p$.
	Moreover, $F$ is a subspace of feasible directions over the set $\gamma_r$ intersected with the simplex.
	Therefore, $\codim(\Sc_{\gamma_r}(p)) \leq d$, and in turn, this implies $\ccdim(\ell) \geq d \geq \codim(\Sc_{\gamma_r}(p))$.
%	If there is a $d$-flat $F$ such that $p \in F \subseteq \gamma_r$, then $\codim(\Sc_{\gamma_r}(p)) \leq d$.
\end{proposition}

In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Lemma~\ref{lem:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.

The feasible subspace dimension bound uses ``local'' information of the property to construct lower bounds, while $d$-flats in Lemma~\ref{lem:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.
In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader than previous bounds for Quadrant 1 from~\citet{ramaswamy2016convex}.

\jessie{Suggest cutting this for space if needed, since it's in the table.}
\paragraph{Example: Variance.}
As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.
In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.

\newpage
\appendix
\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}

@@

\begin{theorem}\label{thm:consistent-implies-indir-elic}
	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
	\jessie{Move to prop; give credit to literature}
\end{theorem}

@@

\section{Implications of convex indirect elicitation bounds}
\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
	Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
	Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.
	Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
	If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
	%and in particular, $\conscvx(\gamma) \geq d + 1$. 
	%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
	%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
	%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
	%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
	%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
	%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$, where $L\in\Lcvx_d$, and let $\Gamma = \prop{L}$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.
	If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\eliccvx(\gamma) \geq d+1$, and recall $\conscvx(\gamma) \geq \eliccvx(\gamma)$ by Corollary~\ref{cor:elic-lb-consis-dim}.
\end{proof}

@@

\section{Notes on calibration}\label{app:calibration}
